### 2019-02-06 Vortrag/slides/sections/cause-effect-chains.tex
More notes and nicer use case sections.
Minor changes.

\subsection{The DD principle as a tool}
\begin{frame}{Using DD to find the reason a program fails}
	\begin{itemize}
		\item The \ddp\ algorithm as described above can be used to find out which part of a certain input is responsible for crashing a program.
		\item From a developers perspective it would be great to know \textit{why} this specific input induces failure.
	\end{itemize}

@@

\begin{frame}{Using DD to find the reason a program fails}
	\begin{alertblock}{Difficulty: Causalities from the input change to the failure}
		A minimal change in the input has major consequences for the program execution. How can the debugger know which chain of effects is responsible for the eventual failure?
	\end{alertblock}

	\pause

@@

\begin{frame}{Delta Debugging on program states}
	\begin{itemize}
		\item A program state is essentially a set of $(variable, value)$ pairs.
		\item A program state of $r_\cmark$ and one of $r_\xmark$ can have the following differences (the deltas): \begin{itemize}
			\item A variable only present in one state
			\item A different value of a variable present in both states
		\end{itemize}
		\item With this the runs $r_\cmark$ and $r_\xmark$ can be compared in different significant locations. 
		\item We use delta debugging to find the current $(variable, value)$ pairs that are responsible for the failure of $r_\xmark$ further down the line.
	\end{itemize}

@@

			\onslide<2->{\begin{enumerate}
				\only<2>{\item A \red{cycle in the RTL tree} of the GCC compiler is created at the 95th hit of \textbf{if\_then\_else\_cond}.}
				\onslide<3>{\item A cycle in the RTL tree of the GCC compiler is created at the 95th hit of \textbf{if\_then\_else\_cond}.} 
				\onslide<3>{\item The \red{cycle produces the error}.}
			\end{enumerate}}
		\end{column}
	\end{columns}
\end{frame}

>>>>

\subsection{Use case 2: Constructing Cause-Effect-Chains}
\begin{frame}{Use case 2: Finding the reason a program fails}
	\begin{itemize}
		\item The \ddp\ algorithm as described above can be used to find out which part of a certain input is responsible for crashing a program.
		\item From a developers perspective it would be great to know \textit{why} this specific input induces failure.
	\end{itemize}

@@

\begin{frame}{Use case 2: Finding the reason a program fails}
	\begin{alertblock}{Difficulty: Causalities from the input change to the failure}
		A minimal change in the input has major consequences for the program execution. How can the debugger know which chain of effects is responsible for the eventual failure?
	\end{alertblock}

	\bigskip
	\pause

@@

\begin{frame}{Delta Debugging on program states}
	\begin{itemize}
		\item A program state is essentially a set of $(variable, value)$ pairs.
		\item A program state of $r_\cmark$ and one of $r_\xmark$ can have the following differences (the deltas): \begin{itemize}
			\item A variable only present in one state
			\item A different value of a variable present in both states
		\end{itemize}
		%\item With this the runs $r_\cmark$ and $r_\xmark$ can be compared in different significant locations. 
		\item We use delta debugging to find the current $(variable, value)$ pairs that are responsible for the failure of $r_\xmark$ further down the line.
	\end{itemize}

@@

			\onslide<2->{\begin{enumerate}
				\only<2>{\item A \red{cycle in the RTL tree} of GCC is created at the 95th hit of \textbf{if\_then\_else\_cond}.}
				\onslide<3>{\item A cycle in the RTL tree of GCC is created at the 95th hit of \textbf{if\_then\_else\_cond}.} 
				\onslide<3>{\item The \red{cycle produces the error}.}
			\end{enumerate}}
		\end{column}
	\end{columns}
\end{frame}
